Left-linear rules in adhesive categories

### 2024-02-11 icalp/fusione.tex
typos

  Consider the pullback of $g_0$ and $f_1$, getting $p_i : P \to D_i$
  ($i \in \{0,1\}$) and the mediating arrows $u_0\colon K_0\to P$ and
  $u_1\colon K_1\to P$ into the pullback given by \Cref{prop:tec} .
  %
  We will say that $(i_0, i_1)$ is a \emph{good independence pair} if
  the first two squares depicted  
  below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ and $u_1 : K_1 \to P$ exists
  \[
    \xymatrix{
      K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
      \ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
       &K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
      \\
      %
      P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
       & P \ar@{.>}[r]_{q_1} & Q_1
    }
  \]
\end{definition}

@@

[Proof~\ref{thNoNeed-proof}

@@

[Proof~\ref{coCanonical-proof}

@@

\begin{lemma}
  \label{le:switch4}
  Let $\der{D}_i$ for $i \in \interval[0]{n+1}$ be derivation sequences
  and consider a switching sequence
  \begin{center}
    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n}\der{D}_n$
  \end{center}
  If the switching sequence does not consists only of inversions,
  there is a shorter switching sequence relating $\der{D}_0$ and
  $\der{D}_0$.
\end{lemma}

@@

\begin{proof}
  Let $\der{D} \shifteq \der{D}'$. Then there is there is a switching
  sequence
  \begin{center}
    $\der{D} = \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n=der{D}'$
  \end{center}
  If it does not consist only of inversions, by Lemma~\ref{le:switchD}
  we can reduce its length by $2$. An inductive reasoning allows us to
  conclude.
\end{proof}

>>>>

  Consider the pullback of $g_0$ and $f_1$, getting $p_i : P \to D_i$
  ($i \in \{0,1\}$) and the mediating arrows $u_0\colon K_0\to P$ and
  $u_1\colon K_1\to P$ into the pullback.\todo{P: tolto ``given by \Cref{prop:tec}'', penso non sia bene avere un riferimento all'appendice qui}
  % given by \Cref{prop:tec} .
  %
  We will say that $(i_0, i_1)$ is a \emph{good independence pair} if
  the first two squares depicted  
  below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ and $u_1 : K_1 \to P$ exists\todo{P: forse si possono togliere i quadrati sotto e dire a parole?}
  \[
    \xymatrix{
      K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
      \ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
       &K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
      \\
      %
      P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
       & P \ar@{.>}[r]_{q_1} & Q_1
    }
  \]
\end{definition}

@@

[Proof~\ref{thNoNeed-proof}]

@@

[Proof~\ref{coCanonical-proof}]

@@

\begin{lemma}
  \label{le:switchD}
  Let $\der{D}_i$ for $i \in \interval[0]{n+1}$ be derivation sequences
  and consider a switching sequence
  \begin{center}
    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n}\der{D}_n$
  \end{center}
  If the switching sequence does not consists only of inversions,
  there is a shorter switching sequence relating $\der{D}_0$ and
  $\der{D}_0$.
\end{lemma}

@@

\begin{proof}
  Let $\der{D} \shifteq \der{D}'$. Then there is there is a switching
  sequence
  \begin{center}
    $\der{D} = \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n=\der{D}'$
  \end{center}
  If it does not consist only of inversions, by Lemma~\ref{le:switchD}
  we can reduce its length by $2$. An inductive reasoning allows us to
  conclude.
\end{proof}
